Modeling Intervention Strategies for United States TB Control

### 2014-02-08 in_progress/presentations/paper/draft.tex
added reference for historical data to initialize model in Methods section
added Q-Q plots to paper

\section{Methods}
\subsection{Basic Structure}
Both the Hill Model (Basic Hill Model) and an extended version of the Hill Model (Extended Hill 
Model) were implemented in 
\texttt{R} as a system of differential equations, which were solved via the
$\texttt{lsoda}$ routine. The systems of differential equations used to capture basic disease dynamics in the Basic Hill Model are shown in Figure 2. In the Extended Hill Model,
more differential equations were implemented to add additional tracking and
economic modeling. These equations are detailed in the Appendix, Section 7.2.

@@

Several other intervention strategies analyzed by the Hill Model were refined
with the Extended Hill, and economic properties about each of them were tracked.
The results for these interventions, which are less effective than curing
entering LTBI cases across the board, are given in the appendix. 
\subsection{Agent Based Evaluation}
The Agent Based Model allowed the statistical properties of the system to be
analyzed and verified. In particular, they illustrated that the deterministic
Hill model provides a robust and consistent statistical measure of TB epidemic
behavior in the US conditions. We found that the distribution of incidence and
final population sizes were normal, with mean accurate to the deterministic
model and standard deviations given in table X, in the Appendix.

@@

@@

\end{document}

>>>>

\section{Methods}
\subsection{Basic Structure}
Both the Hill Model (Basic Hill Model) and an extended version of the Hill Model (Extended Hill 
Model) were implemented in 
\texttt{R} as a system of differential equations, which were solved via the
$\texttt{lsoda}$ routine. The systems of differential equations used to capture basic disease dynamics in the Basic Hill Model are shown in Figure 2. In the Extended Hill Model,
more differential equations were implemented to add additional tracking and
economic modeling. These equations are detailed in the Appendix, Section 7.2. 
Historical data from 2000-2008 was used to initialize the model, which was then run up to the
year 2100.

@@

Several other intervention strategies analyzed by the Hill Model were refined
with the Extended Hill, and economic properties about each of them were tracked.
The results for these interventions, which are less effective than curing
entering LTBI cases across the board, are given in the appendix.

@@

\subsection{Agent Based Evaluation}
The Agent Based Model allowed the statistical properties of the system to be
analyzed and verified. In particular, they illustrated that the deterministic
Hill model provides a robust and consistent statistical measure of TB epidemic
behavior in the US conditions. We found that the distribution of incidence and
final population sizes were normal, with mean accurate to the deterministic
model and standard deviations given in table X, in the Appendix.

@@

\begin{figure}
    \includegraphics[scale=0.4]{figures/qqnormUSBInc.pdf}
    \includegraphics[scale=0.4]{figures/qqnormFBInc.pdf}
    \includegraphics[scale=0.4]{figures/qqnormUSBPop.pdf}
    \includegraphics[scale=0.4]{figures/qqnormFBPop.pdf}
  \caption{Normal Q-Q Plots for 2103 runs of the Stochastic Model with population constant = 1.}
  \label{fig:qqnormPlots}
\end{figure}

Results for USB Incidence, FB Incidence, USB Population, and FB Population in the year
2100 shown, overlayed with linear (normal) fit.
\end{document}
